---
title: "Week 07 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here
)

source(here::here("hw_functions.R"))
```

1.  Describe some of the benefits of using functions.



2.  Practice turning the following code snippets into functions. Think about what each function does. What would you call it? How many arguments does it need? Can you rewrite it to be more expressive or less duplicative?

```{r}
mean(is.na(x))

x / sum(x, na.rm = TRUE)

sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
```

```{r}

```


3.  Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
```



4.  Implement a fizzbuzz function. It takes a single number as input. If the number is divisible by three, it returns "fizz". If it's divisible by five it returns "buzz". If it's divisible by three and five, it returns "fizzbuzz". Otherwise, it returns the number. Make sure you first write working code before you create the function.

```{r}

```


We'll be working with national baby names data from the [Social Security Administration](https://www.ssa.gov/oact/babynames/limits.html)

5. The following code will create your data frame:

```{r US names}
files <- list.files(here::here("Data"), pattern = "\\.txt", full.names = T)

names_df <- map_df(files, ~read_name(.))
```

Describe what the `read_name` function is doing.

6.  Create a function that allows a user to select a name (or names) and graph its trend over time.

* If multiple names are selected, they should each be represented on the graph as a unique color.
* The user should be able to select whether they want to graph based upon the `count` or the `rank` of the name.
* The user should be able to indicate if they are interested in male names, female names, or either.

```{r}

```


7. Create a repository for your course project and share it with @rharrington31. Your project should include:

* A `README.md` file
* A script (whether it is a script or a markdown file) that successfully ingests your data for your analysis.
