---
title: "Week 07 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here,
  rvest
)
```

1. Create regular expressions to find all words that:

- Start with a vowel.
- That only contain consonants. (Hint: thinking about matching “not”-vowels.)
- End with `ed`, but not with `eed.`
- End with `ing` or `ise.`

```{r}

```


2. Create a regular expression that will match telephone numbers as commonly written in the United States.

```{r}

```

We'll be exploring Bob Ross's paintings.

3. Load the CSV of all of his paintings.

```{r}
url <- "https://raw.githubusercontent.com/jwilber/Bob_Ross_Paintings/master/data/bob_ross_paintings.csv"


```

The following code will extract each episode and its air date from the [Joy of Painting Wikipedia page](https://en.wikipedia.org/wiki/The_Joy_of_Painting).

```{r}
jop_url <- "https://en.wikipedia.org/wiki/The_Joy_of_Painting"

webpage <- read_html(jop_url)

elements <- 
  webpage %>% 
  html_elements("li") %>% 
  html_text2() 

episode_list <- elements[str_detect(elements, "([A-Za-z]+ [0-9]{1,2}, [0-9]{4})")]
```

4. Convert `episode_list` into a dataframe such that it includes the following columns:

- `episode`: the name of the episode. Make sure to remove any extra characters (like quotes) and trim whitespace
- `air_date`: the air date of the episode as a date field
- `note`: any additional note

Name this dataframe `episode_list_df`.

```{r}

```

5. Join the `paintings` dataframe to the `episode_list_df` dataframe.

```{r}

```

6. What was Bob Ross's favorite color to paint with in each season of his show? By year?

```{r}

```

7. What words are used most frequently in the titles of his paintings? Did this change over time?

```{r}

```

